One page description

### 2016-12-06 publications/Journal/4-performance.tex
Final changes.
- update plots to use pSim reference in comparison section 4
- list all changes in reply to reviewers file
- A few small changes in section 4 regarding 2nd source of parallelism as mentioned by reviewer.

Signed-off-by: Ben Cardoen <bencardoen@gmail.com>

In this section, we evaluate the performance of different synchronization protocols in \textit{dxex}.
We also compare to \textit{adevs}~\cite{adevs}, currently one of the most efficient simulation kernels~\cite{DEVStoneJournal}, to show that our modularity does not impede performance.
CPU time and memory usage is compared for both single core and multi core simulation.

@@

The benchmarks are run sufficiently long enough to guarantee that the frequency of internal and external transitions is equal within a benchmark, regardless of the randomness of the timeadvance. In our model each model will be executing internal and external transitions, creating an ideal use case to evaluate the speedup inherent parallelism can obtain.
The key difference is that although the event frequency is the same, their concurrency is not. 
Models are equally distributed over the kernels and between threads in \pSim.
The coefficient of variation of our results is less than $1\%$.
The communication overhead is hard to estimate, but given our coefficient of variation, we can expect this overhead to be constant.

>>>>

In this section, we evaluate the performance of different synchronization protocols in \textit{dxex}.
We also compare to \textit{adevs}~\cite{adevs}, currently one of the most efficient simulation kernels~\cite{DEVStoneJournal,DEVSSurvey}, to show that our modularity does not impede performance.
CPU time and memory usage is compared for both single core and multi core simulation.

@@

The benchmarks are run sufficiently long enough to guarantee that the frequency of internal and external transitions is equal within a benchmark, regardless of the randomness of the timeadvance. In our model each model will be executing internal and external transitions, creating an ideal use case to evaluate the speedup inherent parallelism can obtain. 
The key difference is that although the event frequency is the same, their concurrency is not. 
This benchmark combines both possible sources of parallelization : concurrent internal and external transitions. 
Models are equally distributed over the kernels and between threads in \pSim.
The coefficient of variation of our results is less than $1\%$.
The communication overhead is hard to estimate, but given our coefficient of variation, we can expect this overhead to be constant.
